\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-05-25 2-the-cubble-pkg.Rmd
start of section 3

Here we introduce the core functionalities of cubble. The main functions, \code{as_cubble()}, \code{face_spatial()}, \code{face_temporal()}, and \code{unfold()} are described in Section \@ref(create) - \@ref(unfold). Section \@ref(tidyverse) explains the need to create a new class. Section \@ref(compact) will then discusses how cubble relates to existing packages for spatial and temporal data analysis.

>>>>

The main functions in the cubble package are \code{as_cubble()}, \code{face_spatial()}, \code{face_temporal()}, and \code{unfold()}. The following sections explain their role, why the new cubble structure is needed and how the package relates to existing packages for spatial and temporal data analysis.

### 2022-05-25 jss/cubble-jss.tex
start of section 3

Here we introduce the core functionalities of cubble. The main functions, \code{as_cubble()}, \code{face_spatial()}, \code{face_temporal()}, and \code{unfold()} are described in Section \ref{create} - \ref{unfold}. Section \ref{tidyverse} explains the need to create a new class. Section \ref{compact} will then discusses how cubble relates to existing packages for spatial and temporal data analysis.

>>>>

The main functions in the cubble package are \code{as_cubble()}, \code{face_spatial()}, \code{face_temporal()}, and \code{unfold()}. The following sections explain their role, why the new cubble structure is needed and how the package relates to existing packages for spatial and temporal data analysis.
